---
title: "Daily System Metrics - Milwaukee"
output:
  html_document: default
---
<style>
body {
    position: absolute;
    left: 0px;}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo = FALSE}

 table {
    margin-left: 0px;
    margin-right: auto;
 }

td:second-child {
  background-color: yellow;
  text-align:left;
  align: left;
}
th {
  border-top: thin solid black;
  border-bottom: thin solid black;
}


```

```{r color, echo=FALSE, message=FALSE, warning=FALSE}
library(lubridate)
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```

```{r textcolor, echo=FALSE, message=FALSE, warning=FALSE}
colorizetext <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```

**Description:** This report provides a daily snapshot of key system metrics for Milwaukee and Milwaukee Metro areas.  
**Parameter Selection(s):** `r format(Sys.Date()-days(1),"%m/%d/%Y")`  
***`r colorize("Note: Arrived visit volumes include all arrived/completed in-person and telemedicine visits.","blue")`***  
----------------------------------------------------------------------------------------------------------------------------
<br>
<br>
<br>
  
```{r df, echo=FALSE, message=FALSE, warning=FALSE}
source('00_Support_Milwaukee.R')
source('01_Dataframes_Milwaukee.R')
```


```{r clinic_metrics, echo=FALSE, message=FALSE, warning=FALSE}
#clinic_metrics_df,specialty_clinic_metrics_df,community_services_metrics_df,urgent_emergent_metrics_df,bedded_metrics_df,tarp_summary_metrics_df,
#surgery_metrics_df,system_metrics_df

clinic_metrics_table %>%
  mutate(specialty_arrow = case_when(specialty_care_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            specialty_care_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            specialty_care_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            specialty_care_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
    mutate(primary_arrow = case_when(primary_care_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            primary_care_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            primary_care_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            primary_care_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
  select(clinic_metrics2,primary_care_actuals,primary_arrow,primary_care_delta,specialty_care_actuals,specialty_arrow,specialty_care_delta)%>%
  kbl(col.names = NULL, escape = F, centering=F, align='c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Clinic Metrics", "Primary Care"=3, "Specialty Care"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=TRUE,border_right=TRUE)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)#%>%kableExtra::as_image(width=6.5, height=12)
   
```
<br>


```{r specialty_clinic_metrics, echo=FALSE, message=FALSE, warning=FALSE}
#community_services_metrics_df,urgent_emergent_metrics_df,bedded_metrics_df,tarp_summary_metrics_df,
#surgery_metrics_df,system_metrics_df

specialty_clinic_metrics_table %>%
    mutate(mke_campus_arrow2 = case_when(mke_campus_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            mke_campus_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            mke_campus_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            mke_campus_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
    mutate(metro_mke_arrow2 = case_when(metro_mke_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            metro_mke_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            metro_mke_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            metro_mke_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
  select(specialty_clinic_metrics2,mke_campus_actuals,mke_campus_arrow2,mke_campus_delta,metro_mke_actuals,metro_mke_arrow2,metro_mke_delta)%>%
  kbl(col.names = NULL, escape = F, centering=F, align='c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Specialty Clinic Metrics By Location", "Milwaukee Campus"=3, "Metro Milwaukee"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=T,border_right=T)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)#%>%kableExtra::as_image(width=6.5, height=12)
  
   
```
<br>

```{r community_services, echo=FALSE, message=FALSE, warning=FALSE}
#community_services_metrics_df,urgent_emergent_metrics_df,bedded_metrics_df,tarp_summary_metrics_df,
#surgery_metrics_df,system_metrics_df

community_services_metrics_table %>%
    mutate(advocacy_arrow2 = case_when(advocacy_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            advocacy_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            advocacy_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            advocacy_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
    mutate(counseling_arrow2 = case_when(counseling_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            counseling_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            counseling_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            counseling_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
  select(community_services_metrics2,advocacy_actuals,advocacy_arrow2,advocacy_delta,counseling_actuals,counseling_arrow2,counseling_delta)%>%
  kbl(col.names = NULL, escape = F) %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Community Services Metrics", "Advocacy & Protection"=3, "Counseling"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=TRUE,border_right=TRUE)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)#%>%kableExtra::as_image(width=6.5, height=12)
   
``` 
  
<br>

```{r urgent_emergent_metrics, echo=FALSE, message=FALSE, warning=FALSE}
#urgent_emergent_metrics_df,bedded_metrics_df,tarp_summary_metrics_df,
#surgery_metrics_df,system_metrics_df

urgent_emergent_metrics_table %>%
      mutate(urgent_care_arrow2 = case_when(urgent_care_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            urgent_care_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            urgent_care_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            urgent_care_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
    mutate(emergency_arrow2 = case_when(emergency_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            emergency_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            emergency_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            emergency_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
  select(urgent_emergent_metrics2,urgent_care_actuals,urgent_care_arrow2,urgent_care_delta,emergency_actuals,emergency_arrow2,emergency_delta)%>%
  kbl(col.names = NULL, escape = F, align='c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Urgent/Emergent Care Metrics", "Urgent Care"=3, "Emergency"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=TRUE,border_right=TRUE)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)#%>%kableExtra::as_image(width=6, height=10)
   
```
<br>

```{r bedded_metrics, echo=FALSE, message=FALSE, warning=FALSE}
#bedded_metrics_df,tarp_summary_metrics_df,
#surgery_metrics_df,system_metrics_df

bedded_metrics_table %>%
      mutate(mke_bed_arrow2 = case_when(mke_bedded_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            mke_bedded_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            mke_bedded_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            mke_bedded_arrow=='right'~paste0(as.character(fa("arrow-right"))),
            mke_bedded_arrow==" "~ " "))%>%
  select(bedded_metrics2,mke_bedded_actuals,mke_bed_arrow2,mke_bedded_delta)%>%
  kbl(col.names = NULL, escape = F, align = 'c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Census Metrics", "Milwaukee Campus"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=TRUE,border_right=TRUE)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)#%>%kableExtra::as_image(width=4.5, height=18)
   
```
<br>

```{r tarp_summary_metrics, echo=FALSE, message=FALSE, warning=FALSE}
#tarp_summary_metrics_df,
#surgery_metrics_df,system_metrics_df
# for(i in seq_along(tarp_summary_table)) {
#   tarp_summary_table[i, i] <- cell_spec(tarp_summary_table[i, i], "html", color = "blue")
# }


#tarp_summary_table[2, 2] <- cell_spec(tarp_summary_table[2, 2], color = "green", bold = T)

tarp_summary_table %>%
  select(tarp_summary2,census_color,Census,staffing_color,Staffing,RN_Variance)%>%
  mutate(Census= kableExtra::cell_spec(Census, color=case_when((str_contains(tarp_summary2, "NICU") & census_color=="Green"~"green"), (str_contains(tarp_summary2, "NICU") & census_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "NICU") & census_color=="Red")~"red",
(str_contains(tarp_summary2, "PICU") & census_color=="Green")~"green", 
(str_contains(tarp_summary2, "PICU") & census_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "PICU") & census_color=="Red")~"red",
(str_contains(tarp_summary2, "Acute") & census_color=="Green")~"green", 
(str_contains(tarp_summary2, "Acute") & census_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "Acute") & census_color=="Red")~"red", TRUE~"blue"
                                                                   ), bold=TRUE)) %>%
    mutate(Staffing= kableExtra::cell_spec(Staffing, color=case_when((str_contains(tarp_summary2, "NICU") & staffing_color=="Green"~"green"), (str_contains(tarp_summary2, "NICU") & staffing_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "NICU") & staffing_color=="Red")~"red",
(str_contains(tarp_summary2, "PICU") & staffing_color=="Green")~"green", 
(str_contains(tarp_summary2, "PICU") & staffing_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "PICU") & staffing_color=="Red")~"red",
(str_contains(tarp_summary2, "Acute") & staffing_color=="Green")~"green", 
(str_contains(tarp_summary2, "Acute") & staffing_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "Acute") & staffing_color=="Red")~"red", TRUE~"blue"
                                                                   ), bold=TRUE)) %>%
    mutate(RN_Variance= kableExtra::cell_spec(RN_Variance, color=case_when((str_contains(tarp_summary2, "NICU") & staffing_color=="Green"~"green"), (str_contains(tarp_summary2, "NICU") & staffing_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "NICU") & staffing_color=="Red")~"red",
(str_contains(tarp_summary2, "PICU") & staffing_color=="Green")~"green", 
(str_contains(tarp_summary2, "PICU") & staffing_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "PICU") & staffing_color=="Red")~"red",
(str_contains(tarp_summary2, "Acute") & staffing_color=="Green")~"green", 
(str_contains(tarp_summary2, "Acute") & staffing_color=="Yellow")~"yellow",
(str_contains(tarp_summary2, "Acute") & staffing_color=="Red")~"red", TRUE~"blue"
                                                                   ), bold=TRUE)) %>%
  select(-census_color, -staffing_color)%>%
  kbl(col.names = NULL, escape = F, align = 'c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("TARP Summary - All Bedded", "Census", "Staffing", "RN Variance"),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=TRUE,border_right=TRUE)#%>%kableExtra::as_image(width=4.25, height=2.75)
   
```
<br>

```{r surgery_metrics, echo=FALSE, message=FALSE, warning=FALSE}
#surgery_metrics_df,system_metrics_df

surgery_metrics_table %>%
        mutate(mke_campus_arrow2 = case_when(mke_campus_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            mke_campus_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            mke_campus_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            mke_campus_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
    mutate(surgicenter_arrow2 = case_when(surgicenter_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            surgicenter_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            surgicenter_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            surgicenter_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
  select(surgery_metrics2 ,mke_campus_actuals,mke_campus_arrow2,mke_campus_delta,surgicenter_actuals,surgicenter_arrow2,surgicenter_delta)%>%
  kbl(col.names = NULL, escape = F, align = 'c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Surgical Metrics", "Milwaukee Campus"=3, "Surgicenter"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=TRUE,border_right=TRUE)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)#%>%
#kableExtra::as_image(width=5.5, height=7)

```
<br>

```{r system_metrics, echo=FALSE, message=FALSE, warning=FALSE}
#system_metrics_df

system_metrics_table %>%
  select(system_metrics2,mke_campus_actuals)%>%
  kbl(col.names = NULL, escape = F, align = 'l') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals")),bold=T, underline=T, font_size = 10, align="left")%>%
  add_header_above(c("System Metrics"=2),bold=T, underline=T, font_size = 14, background="lightgray", align="left", border_left=TRUE,border_right=TRUE)#%>%kableExtra::as_image(width=8, height=5.5)

   
```
<br>
Link to Report Methodology Job Aid: <a href="https://insight.chw.org/TrainingCenter/Shared%20Documents/Report%20Center%20Training%20Materials/Daily%20System%20Metrics/Daily%20System%20Metrics.pdf">Daily System Metrics Methodology</a>
<br>
If you have any questions, please contact: insight@chw.org


<br>

```{r create_email, echo=FALSE, message=FALSE}
 library(blastula)
#  #Use the document created to send via RStudio Connect
render_connect_email(input = "03_DailySystemMetricsMilwaukeeEmail.Rmd",
                                           connect_footer = FALSE) %>%
   attach_connect_email(
     subject = "Daily System Metrics - Milwaukee",
     attach_output = FALSE,
     attachments = NULL,
     preview=TRUE
   )