---
title: "Daily System Metrics - Fox Valley"
output: html_document
---

<style>
body {
    position: absolute;
    left: 0px;}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo = FALSE}

 table {
    margin-left: 0px;
    margin-right: auto;
 }

td:second-child {
  background-color: yellow;
  text-align:left;
  align: left;
}
th {
  border-top: thin solid black;
  border-bottom: thin solid black;
}


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(lubridate)
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```

**Description:** This report provides a daily snapshot of key system metrics for Fox Valley and Fox Valley Metro areas.  
**Parameter Selection(s):** `r format(Sys.Date()-days(1),"%m/%d/%Y")`  
***`r colorize("Note: Arrived visit volumes include all arrived/completed in-person and telemedicine visits.","blue")`***  
----------------------------------------------------------------------------------------------------------------------------
<br>
<br>
<br>
  
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('00_Support_Fox_Valley.R')
source('01_Dataframes_Fox_Valley.R')
```

```{r specialty_clinic_metrics, echo=FALSE, message=FALSE, warning=FALSE}
fvspecialty_clinic_metrics_table %>%
    mutate(fv_campus_arrow2 = case_when(fv_campus_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            fv_campus_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            fv_campus_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            fv_campus_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
    mutate(metro_fv_arrow2 = case_when(metro_fv_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            metro_fv_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            metro_fv_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            metro_fv_arrow=='right'~paste0(as.character(fa("arrow-right")))))%>%
  select(specialty_clinic_metrics2,fv_campus_actuals,fv_campus_arrow2,fv_campus_delta,metro_fv_actuals,metro_fv_arrow2,metro_fv_delta)%>%
  kbl(col.names = NULL, escape = F, centering=F, align='c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*"),
                          paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Specialty Clinic Metrics By Location", "Fox Valley Campus"=3, "Metro Fox Valley"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=T,border_right=T)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)
  
   
```
<br>
```{r bedded_metrics, echo=FALSE, message=FALSE, warning=FALSE}
fvbedded_metrics_table %>%
      mutate(fv_bed_arrow2 = case_when(fv_bedded_arrow=='up'~paste0(as.character(fa("arrow-up"))),
            fv_bedded_arrow=='down'~paste0(as.character(fa("arrow-down"))),
            fv_bedded_arrow=='left'~paste0(as.character(fa("arrow-left"))),
            fv_bedded_arrow=='right'~paste0(as.character(fa("arrow-right"))),
            fv_bedded_arrow==" "~ " "))%>%
  select(bedded_metrics2,fv_bedded_actuals,fv_bed_arrow2,fv_bedded_delta)%>%
  kbl(col.names = NULL, escape = F, align = 'c') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals"),"",
                          paste0("%","$\\Delta$", " from Prior \nTime Period*")),bold=T, underline=T, font_size = 10, align="center")%>%
  add_header_above(c("Census Metrics", "Fox Valley Campus"=3),bold=T, underline=T, font_size = 14, background="lightgray", align="center", border_left=TRUE,border_right=TRUE)%>%
footnote(
    general = c(
      paste0("<small>*Scheduled visits reflect ", format(Sys.Date(),"%m/%d/%y")," and is compared to the prior 5 ", weekdays(Sys.Date()),"s</small>")
    ),
    footnote_as_chunk = T ,
    escape = F
)
   
```
<br>
```{r experience_metrics, echo=FALSE, message=FALSE, warning=FALSE}
experience_metrics_table %>%
  select(experience_metrics2,fv_campus_actuals)%>%
  kbl(col.names = NULL, escape = F, align = 'l') %>%
  kable_paper(full_width = F, html_font = "Arial", position="left")%>%
  add_header_above(c(" ", paste0(format(Sys.Date()-days(1),"%m/%d/%y"), " \nActuals")),bold=T, underline=T, font_size = 10, align="left")%>%
  add_header_above(c("Experience Metrics"=2),bold=T, underline=T, font_size = 14, background="lightgray", align="left", border_left=TRUE,border_right=TRUE)

   
```
<br>
Link to Report Methodology Job Aid: <a href="https://insight.chw.org/TrainingCenter/Shared%20Documents/Report%20Center%20Training%20Materials/Daily%20System%20Metrics/Daily%20System%20Metrics.pdf">Daily System Metrics Methodology</a>
<br>
If you have any questions, please contact: insight@chw.org

<br>

```{r create_email, echo=FALSE, message=FALSE}
library(blastula)
# Use the document created to send via RStudio Connect
render_connect_email(input = "03_DailySystemMetricsFoxValleyEmail.Rmd",
                    connect_footer = FALSE) %>%
  attach_connect_email(
    subject = "Daily System Metrics - Fox Valley",
    attach_output = FALSE,
    attachments = NULL,
    preview=TRUE
  )